### 2016-07-10 version0.0/intro0.0.tex
Update intro0.0.tex
edits to stellar mass section up to but not including dynamical mass

\section{Stellar mass}
\label{sec: starmass_intro}
One of the most fundamental physical parameters which describes the present state of the galaxies is stellar mass. 
Stellar mass is linked with the structure and star formation history of disc galaxies~\citep{Gavvazi96} and all morphologies~\citep{Scodeggio02}. 
In order to determine stellar population in spiral galaxies, the mean stellar mass density of a galaxy may be a more basic parameter than the total stellar mass~\citep{Bell00}. 
\cite{Kauffmann03} tested that on more than 100,000 galaxies observed by Sloan Digital Sky Survey~\citep[SDSS;][]{York00}. 
They also showed that these results are applied for all morphological types.

Measuring the mass of the stellar population is indirect and subject to significant uncertainties. 
In principle there are two ways to measure stellar mass in galaxies. 
First is measuring the dynamical mass of galaxies using kinematics~\citep{Cappellari06} or lensing~\citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass. 
This method has been successful to predict and subtract the mass of the dark matter, which is the dominant mass in galaxies~\citep{Zaritsky94}, and can easily cause uncertainties as high as the order of the measurement.

The second method is based on stellar population models~\citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, like luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations. 
This method has uncertainties too, and one must also model the uncertainties. 
Uncertainties come from uncertainties in the stellar initial mass function (see Sec.~\ref{sec: imf}), the stellar evolution models, especially the stage where they have most luminosity in their evolution, and the evolutionary state of galaxy~\citep[see,][]{Dalcanton12}, and star formation histories.

In order to translate between photometry and dynamics the stellar mass to light ratio (M/L) is needed. 
Measuring the accurate M/L can easily lead us to stellar mass surface density.  
To do that, the M/L by can be measured using scale relation between them, from different colours and then multiply it by the surface brightness to calculate the local surface stellar mass density. 
The M/L scale relations make a connection between two methods of measuring stellar mass~\citep{Bell03}. 
These relations are indirect methods for measuring the stellar masses and have high uncertainties in specific cases, but they help to study the stellar mass in large samples. 
This is one of the solution to the problem of the measuring the stellar mass within galaxies. 
As a result it is important to check the accuracy of total stellar mass estimations and provide methods, which measure and produce a map of the stellar mass surface density distribution in galaxies. 
This method gives more accurate result than measuring the stellar mass surface density distribution from single-band images rescaled by uniform mass to light ratio~\citep{Zibetti09}.

Having two independent methods to measure stellar mass helps to compare the results and check whether there are any systematic differences. 
Comparing the results from measuring stellar mass in stellar clusters shows there is no huge difference. 
Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few x10 per cent, so one should be more careful to model subtleties~\citep{McLaughlin05}.

\subsection{Dynamical Mass}
The mass distribution in disk galaxies is usually calculated from rotation curves or integrated line profiles from emission lines such as H${\alpha}$, CO, and \hi lines. 
Thanks to the current generation of detectors, the \halpha and CO lines have very high-resolution spectra over most of the optical disk, and cover most regions in the sky. 
Integrated line widths only yield an estimate of a total mass within some (uncertain) isophotal radius.

>>>>

\section{Stellar mass}
\label{sec: starmass_intro}
One of the most fundamental physical parameters which describes the present state of a galaxy is its stellar mass. 
Stellar mass is linked with the structure and star formation history of disc galaxies~\citep{Gavvazi96} and all morphologies~\citep{Scodeggio02}. 
In order to determine the stellar populations of spiral galaxies, the mean stellar mass density of a galaxy may be a more basic parameter than the total stellar mass~\citep{Bell00}. 
\cite{Kauffmann03} tested that on more than 100,000 galaxies observed by the Sloan Digital Sky Survey~\citep[SDSS;][]{York00}. %PB: what is "that"?
They also showed that these results applied to all morphological types. %PB: what are "these results" ?

Measuring the mass of a stellar population is indirect and subject to significant uncertainties. 
In principle there are two ways to measure stellar mass in galaxies. 
The first is measuring the dynamical mass of a galaxy using kinematics~\citep{Cappellari06} or lensing~\citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass. %PB: "kinematics" and "lensing" are astro-jargon: please explain a bit more
This method has been successful to predict and subtract the mass of the dark matter, which is the dominant mass in galaxies~\citep{Zaritsky94}, and can easily cause uncertainties as high as the order of the measurement. %PB: but is it successful in measuring the stellar mass?

The second method is based on stellar population models~\citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, such as luminosity in different wavelengths, colours, or spectral energy distribution. 
This method has uncertainties too, and one must also model the uncertainties. %PB: sentence not useful.
Uncertainties come from uncertainties in the stellar initial mass function (see Sec.~\ref{sec: imf}), the stellar evolution models, especially the stage where stars have the most luminosity in their evolution, the evolutionary state of the galaxy~\citep[see,][]{Dalcanton12}, and star formation histories.

%PB: this paragraph was very difficult to understand and I did a lot of rewriting. Please check.
In order to translate between photometry and dynamics the stellar mass-to-light ratio ($M/L$) is needed. %PB: is this the first method or the second one? It's not really about dynamics.
The use of $M/L$ is one way to measure stellar mass surface density. It is an indirect method and has high uncertainties in specific cases, but can help to study the stellar mass in large samples. 
For integrated galaxy light, the $M/L$ is estimated using scaling relations between $M/L$ and broadband colours \citep[e.g.]{Bell03} and then multiplied by luminosity to estimate a mass.
For resolved galaxies, one can produce a map of the stellar mass surface density distribution in galaxies using resolved colour to measure spatial variations in $M/L$.
This method gives more accurate results than measuring the stellar mass surface density distribution from single-band images rescaled by a uniform mass to light ratio~\citep{Zibetti09}.

Having two independent methods to measure stellar mass helps to check whether there are any systematic differences. 
Comparing the results from measuring stellar mass in stellar clusters shows there is no huge difference. %PB: ref?
Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few x10 per cent, so one should be careful to model subtleties~\citep{McLaughlin05}.

\subsection{Dynamical Mass}
The mass distribution in disk galaxies is usually calculated from rotation curves or integrated line profiles from emission lines such as H${\alpha}$, CO, and \hi lines. 
Thanks to the current generation of detectors, it is possible to obtain  very high-resolution spectra in the \halpha and CO lines  over most of the optical disks of galaxies. % and cover most regions in the sky. PB: not sure about "most regions of sky"
Integrated line widths only yield an estimate of a total mass within some (uncertain) isophotal radius.
